First Order Alternation

### 2018-09-20 quantifiers/draft.tex
ok

A lazy annotation semi-algorithm can stop and report emptiness if it
succeeds in building a closed and safe unfolding of the automaton. For
instance, the \impact~ semi-algorithm \cite{McMillan06}

The higher complexity of the first-order alternating automata model
versus the automata considered in \cite{IosifXu18}, which uses boolean
constants for control states and whose transition rules have no
quantifiers, manifests itself within the method used to generate the
labels of the unfolding, which is discussed in the rest of this
section.

>>>>

A lazy annotation semi-algorithm will stop and report emptiness
provided that it succeeds in building a closed and safe unfolding of
the automaton. For instance, the \impact~ semi-algorithm
\cite{McMillan06} upon which our procedure is based, continuosly
expands the domain of the unfolding, while partially recomputing its
labeling and the coverage, and stops when a safe complete unfolding
has been found. The following theorem proves the soundness of this
method:

\begin{theorem}\label{thm:soundness}
  Given an automaton $\A$, if $\A$ has a nonempty safe closed
  unfolding then $\lang{A} = \emptyset$. 
\end{theorem}
\proof{

\qed}

As mentioned above, we check emptiness of first-order alternating
automata using the same method previously used to check emptiness of a
simpler model of alternating automata, which uses boolean constants
for control states and whose transition rules have no quantifiers
\cite{IosifXu18}. The higher complexity of the automata model
considered here, manifests itself within the interpolant generation
procedure, used to label the unfoldings. We shall discuss generation
of interpolants in the remainder of this section.
